%resume.tex template from link at
%http://mboedick.org/code/latex_resume_tips.php
\documentclass[11pt,a4paper]{article}
\usepackage{fullpage}
\pagestyle{empty}
\begin{document}
\begin{tabular*}{160mm}{l@{\extracolsep{\fill}}r}
  \textbf{Date} & \today \\
  \textbf{Name} & {\large \textbf{Dr Matthew McDonnell}} \\
  \textbf{Address} & Department of Physics\\
  & Clarendon Laboratory \\
  & Oxford OX1 3PU \\
  \textbf{Phone} & (Old phone)\\
  \textbf{email} & (Old email)\\
  \textbf{Nationality} & Australian\\
\end{tabular*}
\vspace{0.1in}
\\
{\large \textbf{Employment History}}
\begin{itemize}
  \item
    \begin{tabular*}{140mm}{l@{\extracolsep{\fill}}l}
      \textbf{July 2003--Present} & Postdoctoral Research Assistant in
      the Ion Trap\\
      &  Quantum Information Processor group\\
      & (University of Oxford)
    \end{tabular*}
  \item
    \begin{tabular*}{140mm}{l@{\extracolsep{\fill}}l}
      \textbf{January 1999--July 1999} & Research Engineer at Special
      Research Centre\\
      & for Advanced Mineral and Material Processing \\
      & (University of Western Australia)
    \end{tabular*}
\end{itemize}
%\vspace{0.1in}
{\large \textbf{Education}}
\begin{itemize}
  \item
    \begin{tabular*}{140mm}{l@{\extracolsep{\fill}}r}
      \textbf{October 1999--June 2003} & \textbf{University of Oxford}
    \end{tabular*}
    \\
    \begin{tabular*}{140mm}{l}
      DPhil in Atomic and Laser Physics \\
      Thesis title ``Two-Photon Readout Methods for\\
      an Ion Trap Quantum Information Processor'' \\
    \end{tabular*}
  \item
    \begin{tabular*}{140mm}{l@{\extracolsep{\fill}}r}
      \textbf{February 1993--November 1998} & 
      \textbf{University of Western Australia}\\
      BSc (Chemical Physics) (hons. 1st Class)& \\
      BE (Materials) (hons. 1st Class)&\\
    \end{tabular*}
    \\
    \begin{tabular*}{140mm}{ll}
      \textbf{Prizes:}\\
         1993: & Lady James Prize in Chemistry (shared), Shell Prize in
         Science, \\
         & Bradken Prize in Materials Engineering\\
         1994: & UWA Graduates Association Prize in Science\\
         1995: & Cape Bouvard Prize in Materials Engineering, \\
         & Lady James Prize in Physical Science (shared)\\
        1996: & Faculty of Science Medal for best Honours Science
        Student,\\
        & J.A. Wood Memorial Prize for best Honours Student in\\
        & the Faculties of Science, Engineering, Medicine, Agriculture
        and Dentistry\\
         1997: & Centre for Water Research Prize\\
         1998: & Rojan Advanced Ceramics Prize in Materials
         Engineering\\
         1999: & Awarded a Commonwealth Scholarship to study for\\
         & a DPhil at the University of Oxford
    \end{tabular*}

%   \item
%     \begin{tabular*}{140mm}{l@{\extracolsep{\fill}}r}
%       February 1988--November 1992 & Duncraig Seniour High School\\
%       TEE Subjects:  Applicable Mathematics, Calculus, &\\
%       Chemistry, Computing, Physics, English Literature &
%     \end{tabular*}
\end{itemize}
%
%
%\vspace{0.1in}
%
%
%\vspace{0.1in}
{\large \textbf{Publications}}
%\begin{tabular*}{140mm}{l}
\begin{itemize}
  \item `` Laser linewidth effects in quantum state discrimination by
    electromagnetically induced transparency'',  McDonnell MJ,
    Stacey DN, and Steane AM, \textit{Phys. Rev. A} \textbf{70}
    053802 (2004) 
  \item ``High-efficiency detection of a single quantum of angular
    momentum by suppression of optical pumping'',  McDonnell MJ,
    Stacey JP, Webster SC, Home JP, Ramos A, Lucas DM, Stacey DN,
    Steane AM, 
    \textit{Phys. Rev. Lett.} \textbf{93} 153601 (2004)
  \item ``Isotope-selective photoionization for calcium ion
    trapping'', Lucas DM, Ramos A, Home JP, McDonnell MJ, Nakayama S,
    Stacey JP, Webster SC, Stacey DN, Steane AM,
    \textit{Phys. Rev. A} \textbf{69} 012711 (2004)
  \item ``Oxford Ion Trap Quantum Computing Project'', Lucas DM, Donald CJS,
    Home JP, McDonnell M, Ramos A, Stacey DN, Stacey JP, Steane AM,
    Webster SC, \textit{Phil. Tans. R. Soc. Lond. A} \textbf{361} 1401
    (2003)
  \item ``Search for correlation effects in linear chains of trapped
    Ca$^{+}$ ions'', Donald CJS, Lucas DM, Barton PA, McDonnell MJ,
    Stacey JP, Stevens DA, Stacey DN, Steane AM,
    \textit{Europhys. Lett.} \textbf{51} 388--394 (2000)
  \item ``Magnetisation of thin films under oblique field
    conditions'', McDonnell M, Street R, Woodward RC, Chapman JN,
    \textit{J. Magnetism and Magnetic Materials} \textbf{177}
    1281--1282 (1998)
  \item ``Photocurrent autocorrelation of femtosecond laser pulses in
    poly(p-phenylene vinylene)'', Samoc M, Samoc A, Luther-Davies B,
    Dowd A, McDonnell M, \textit{J. Phys. D} \textbf{30} 895--899 (1997)
\end{itemize}
%\end{tabular*}
%
%
%\vspace{0.1in}
%\pagebreak
{\large \textbf{Research Interests}}
\begin{itemize}
\item For the last 5 years I have been involved in an ion trap quantum
  information experiment at the University of Oxford.  The goal of
  this research has been to control and measure the quantum behaviour
  of individual ions of calcium trapped in an ion trap, in order to
  construct the fundamental building blocks of a quantum information
  processing system.  The experimental work has involved laser
  cooling, computer control of experiments and the design and
  construction of optical systems.  The theoretical side of the work
  has involved simulation of the atomic and optical systems using
  programming languages such as \textit{Matlab} and \textit{Mathematica}. 
\item I am interested in applying the techniques I have learnt over
  the course of my career to interdisciplinary areas of science 
  such as nanotechnology and biophysical systems.
\end{itemize}


{\large \textbf{Skills}}
\begin{itemize}
  \item Experimental atomic physics, in particular frequency
    stabilisation of infrared and ultraviolet diode lasers, and  
    ion trap experiments. 
  \item Experience with a wide range of experimental techniques including
    TEM, SEM, AFM, Kerr microscopy, materials testing and analytical chemistry
    techniques.
  \item Numerical simulation of the evolution of atomic systems using
    \textit{Matlab}.
   \item Teaching experience ranging from laboratory demonstrating for groups
    of 10-20 students to Oxford tutorial teaching for groups of 
    2-7 students. 
  \item Good computer skills. Proficient in the use of Windows
    (95/98/2000/NT/XP) and UNIX (Solaris, Linux, FreeBSD) operating
    systems.
  \item Document preparation: \LaTeX, Xfig, Word, Excel, Powerpoint,
    HTML.
  \item Programming languages:  \textit{Matlab}, \textit{Mathematica},
    Ocaml, C, \textit{Labview}, Pascal, Perl, Java.
\end{itemize}
%
%
% {\large \textbf{References}}
% %(Available on request)
\end{document}
